%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{verbatim}



\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{\huge{Fernando}}{\huge{ de \color{white}{Oliveira Lima}}}{Software/Hardware Developer | Electrical Engineer} % Your name and current job title/field


\vspace{1cm}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------
 
\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
Luis Inglesias, 120, apt 108
Rio de Janeiro, RJ
22795--060
(21) 98821-4779
\href{mailto:folivelima@gmail.com}{folivelima@gmail.com}
\href{https://www.linkedin.com/in/fernando-lima-47673263/}{in://fernando.oliveira}
\href{https://github.com/fol21}{github/fol21}
\section{Languages}
Fluent English
Fluent Portuguese
Basic Spanish
\section{Code}
\item Node.js, Javascript
\item Typescript
\item C/C++
\item Python
\item Angular, Ionic, React
\item C\# /.NET, .NET Core
\item Java, Spring
\item HTML5,CSS3, SCSS
\section{Tools}
\item Linux \& Microsoft
\item Azure, Google Cloud, IBM Cloud
\item Git, Gitlab, Github, SourceTree
\item Desenvolvimento de Android apps
\item KiCAD, Eagle
\item Espressif, Arduino, Sistemas Embarcados
\item Photoshop, Lightroom
\end{aside}


\section{Profile}

Experienced in Software and Hardware development, with activities in the areas of Internet of Things, Web dev, Software, Image Processing among others, besides having interest in Machine Learning and Blockchain, Image and Data Processing, Web.

Has personal projects involving Internet tools of Things, embedded and Web Applications, implemented using tools like Node.js and interfaces in Angular, React.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

%------------------------------------------------

\entry
{03/2012--10/2018}
{\hspace{.25cm} Bachelor of Science in Electrical Engineering}
{\\Universidade do Estado do Rio de Janeiro (UERJ), Rio de Janeiro, Brazil}
{Graduated  in Rio de Janeiro ,Brazil.  \\ \color{red}{CR = 7.8/10} }

%------------------------------------------------

\entry
{08/2015--05/2016}
{\hspace{.25cm} Exchange Program in Bachelor of Electrical Engineering, Marietta, USA}
{\\Kennesaw State University - Marietta Campus}
{Exchange undergraduate student through the period of two semesters in Kennesaw State University.  \\
\color{red}{GPA = 3.9/4.0} }

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}

%------------------------------------------------

\entry
{10/2018--}
{\hspace{.15cm} Radix Engenharia e Software}
{Rio de Janeiro, Brasil}
{Trainee \\
Works in Software projects and web systems. Using Node.js, Angular, C ++, C \ #, Java, Python, among others.}

\entry
{11/2016--10/2018}
{\hspace{.15cm} Radix Engenharia e Software}
{Rio de Janeiro, Brasil}
{Intern \\
Worked in innovation projects and web systems, IoT and Cognitive Computing. Using Node.js, Angular, C ++, C \ #, Java, Python, among others.}

\entry
{06/2016--08/2016}
{\hspace{.15cm} University of California, San Diego}
{San Diego, EUA}
{Research Exchange Program \\
Worked as visiting scholar at UCSD, in a Image Processing and mobile development project for monitoring the status of surgical incisions.}


\entry
{08/2013--08/2015}
{\hspace{.15cm}National Institute of Space Research (INPE)}
{Rio de Janeiro, Brazil}
{Undergraduate Researcher \\
Was part of a scientific initiation program as an undergraduate researcher. Worked at PROSAICO (Processing of Signals,Applied Intelligence and Communications Laboratory) at UERJ, with cooperation of the National Institute of Space Research (INPE) in a specific research of spectral filtering of high frequency noises in the Eta atmospheric model data.}

\end{entrylist}

\begin{entrylist}
\entry
{08/2012--03/2013}
{\hspace{.15cm}Universidade do Estado do Rio de Janeiro (UERJ)}
{Rio de Janeiro, Brazil}
{Laboratory Technician \\
Worked as a technician in PROSAICO (Processing of Signals,Applied Intelligence and Communications Laboratory), in maintenance of equipments and computers and developing improvements.}

\end{entrylist}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Courses and other activities}

\begin{entrylist}

%------------------------------------------------



\entry
{01/2014 -- Present}
{\hspace{.15cm}Founder of UERJBotz Robotics team}
{Universidade do Estado do Rio de Janeiro}
{Is one of the founding members of UERJbotz, a robotics competition team that make it's debut in 2014.}

\entry
{03/2012 -- Present}
{\hspace{.15cm}IEEEXtreme competitor}
{IEEE}
{Competes once a year in the programming marathon iEEEXtreme, since 2012.}

\entry
{08/2012 -- 12/2012}
{\hspace{.15cm}Course - Control of Mobile Robots}
{Coursera, Georgia Institute of Technology}
{Completed the online course about control theory applied to mobile robots.}

\entry
{01/2017}
{\hspace{.15cm}Certificados na Udemy}
{Udemy}
{\begin{itemize}
\item Advanced C++
\item C#
\item C++ Concurrency
\item Node.js
\item Angular
\item Ionic
\item React, React-Native
\item Full Stack Development, TDD
\item Blockchain
\end{itemize}}

\entry
{07/2017 -- }
{\hspace{.15cm} Chair of  IEEE UERJ Student Branch}
{Universidade do Estado do Rio de Janeiro}
{A Student Branch is an IEEE related initiative of Students for projects in the area of ​​Engineering (mainly Electrical and Computing) for professional development and Projects of Innovation and learning.
}

\entry
{22/2018 --26/2018}
{\hspace{.15cm} Chief Coordinator of VI Electrical Engineering Week }
{Universidade do Estado do Rio de Janeiro}
{A Week of presentations and courses in the areas of Power, Electronics and Software. Happened between  22/10 -- 26/10/ 2018.}

\entry
{01/2018}
{\hspace{.15cm}Hackton Stefanini, competidor}
{}
{WINNER OF Hackton da Stefanini . Developer.}

\entry
{03/2018 }
{\hspace{.15cm}Hackton Rio2C, competidor}
{}
{Finalist of Hackton Rio2C. Developer.}

\entry
{04/2018 }
{\hspace{.15cm}Hackton Globo, competidor}
{}
{Competitor of Hackton Globo . Developer.}


%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\begin{comment}
\section{publications}

\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

\printbibsection{book}{books} % Print all books from the bibliography

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=bibheading]
\end{refsection}

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=bibheading]
\end{refsection}

\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

\printbibsection{report}{research reports} % Print all research reports from the bibliography
\end{comment}
%----------------------------------------------------------------------------------------

\end{document}